---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# pathmodelfit

<!-- badges: start -->
[![R build status](https://github.com/tmsalab/pathmodelfit/workflows/R-CMD-check/badge.svg)](https://github.com/tmsalab/pathmodelfit/actions)
[![Package-License](http://img.shields.io/badge/license-GPL%20(%3E=2)-brightgreen.svg?style=flat)](http://www.gnu.org/licenses/gpl-2.0.html)
<!-- badges: end -->

The goal of `pathmodelfit` is to provide fit indices for the path components of
latent variable Structural Equation Models (SEM).

## Installation

You can install the released version of pathmodelfit from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("pathmodelfit")
```

Or, you can be on the cutting-edge development version on [GitHub](https://github.com/) using:

``` r
if(!requireNamespace("remotes")) { install.packages("remotes") }
remotes::install_github("tmsalab/pathmodelfit")
```

## Usage

To use `pathmodelfit`, load the package using:

```{r example, eval = FALSE}
library("pathmodelfit")
```

## Authors

Steven Andrew Culpepper and Larry Williams

## Citing the `pathmodelfit` package

To ensure future development of the package, please cite `pathmodelfit`
package if used during an analysis or simulation study. Citation information
for the package may be acquired by using in *R*:

```{r, eval = FALSE}
citation("pathmodelfit")
```

## License

GPL (>= 2)
